### 2020-07-10 msr.tex
Katy comment edits

In spite of this setback, research into \glspl{MSR} continued through the late
1970s. In 1980, \gls{ORNL} published a report describing a new \gls{MSR}
concept, called the \gls{DMSR} \cite{gehin_liquid_2016} with denatured
$^{235}$U fuel (i.e. low-enriched uranium). The \gls{ORNL} researchers
developed this design in response to the fuel reprocessing restrictions
introduced by President Ford in 1976. The \gls{DMSR} would operate as a
once-through
converter system without fuel reprocessing. While the fuel consists of 19.75
\% high-assay low-enriched uranium, the initial core loading includes thorium
to boost its conversion ratio throughout its lifetime. It has a continuous
online feed consisting of \gls{HALEU} to maintain criticality, and denatured
$^{235}$U to keep uranium enrichment levels below nuclear non-proliferation
policy thresholds. The design also includes a gas sparging system for removing
gaseous fission products, while noble metals plate out onto the walls of
the coolant loop. The older \gls{MSBR} design had a significant drawback; the
extensive neutron damage in the graphite moderator necessitated frequent
replacement (every four years) throughout its operational lifetime. The
\gls{DMSR} avoids this issue by having a lower power density while maintaining
the overall power output of 2250 MW$_{\text{th}}$. As a result, researchers
projected that the graphite moderator would last for the entirety of the
\gls{DMSR}'s design lifetime.

There was a concurrent program at the UK Atomic Energy Authority for the
development of a 2500 MW$_{\text{e}}$ lead-cooled Molten Chloride Fast Reactor
concept \cite{smith_assessment_1974}. It is a dual fluid system,
with separate loops for the fuel salt and the blanket salt. The blanket is a
1 m-wide tank surrounding the core. The absence of moderators and the choice
of chloride over fluoride salt resulted in a relatively hard neutron spectrum
which favors $^{239}$Pu breeding over the thorium cycle. The UK researchers
performed some experiments to study molten salt chemistry but there were no
reactor prototypes. The UK program eventually shut down just like its
US counterpart partly due to the successful demonstration of the Prototype
Fast Reactor which had achieved criticality in 1974.

Following a lull lasting through the late 20th century, \gls{MSR} research
picked up pace due to renewed interest initiated by the Generation IV Forum in
2001. Today, various national and commercial bodies are developing numerous
\gls{MSR} concepts.

@@

The various \gls{MSR} designs under development today illustrate the
flexibility of this reactor concept. Graphite-moderated thermal-spectrum
\glspl{MSR} are typically straightforward \gls{LEU} burners or
$^{232}$Th/$^{233}$U iso-breeders/breeders, while epithermal- and
fast-spectrum \glspl{MSR} can operate as \gls{TRU} fuel burners or
$^{238}$U/$^{239}$Pu breeders. Breeder designs can be further categorized into
one- or two-fluid designs. Two-fluid designs feature separate blanket molten
salt mixtures that contain higher proportions of fertile material than the
fuel salt mixture. Examples of one-fluid designs include the Integral Molten
Salt Reactor from Terrestrial Energy \cite{leblanc_integral_2015} and the
\gls{MSR} design from Transatomic Power
\cite{transatomic_power_corporation_technical_2016} while two-fluid designs
include the \gls{MSFR} \cite{serp_molten_2014} and \gls{MOSART}
\cite{ignatiev_molten_2014}.

@@

Economic analyses of \glspl{MSR} are preliminary at the current
stage of \gls{MSR} development. Qualitatively, many technical factors favor
\glspl{MSR} over \glspl{LWR}. Some of these factors include: smaller reactor
core size due to low operating pressures, higher thermal efficiency and
cheaper air-cooling systems due to high operating temperatures, reduction in
fuel fabrication costs, and shorter reactor shutdown periods due to online
refueling \cite{dolan_1_2017}. Moir \cite{moir_recommendations_2008}
published data from \gls{ORNL} reports on the estimated electricity costs for
a 1000 MWe \gls{MSR} with 20\% enriched $^{235}$U fuel and no reprocessing
throughout the reactor's 30-year lifetime. Adjusted to year 2000 dollars, the
electricity costs for this type of \gls{MSR} was 7\% and 8\% lower than that
of pressurized water reactors and coal power plants. These differences are
within the $\pm$10\% uncertainty range but Moir remains optimistic.
The author also notes that costs could be lower in an \gls{MSR} with
fertile feed and online reprocessing could reach fuel self sufficiency.

In terms of technological readiness, \glspl{MSR} still require significant
research efforts and engineering demonstrations for experimental validation of
various components before a full commercial model can be commissioned. Work
towards creating a safety and licensing framework for \glspl{MSR} has picked
up pace only in recent years due to the growing interest from commercial
\gls{MSR} developers.

@@

In the past two decades, researchers have developed several
new tools for simulating steady-state and transient behavior in \glspl{MSR}.
Many earlier efforts featured simplifications in simulating
thermal-hydraulics by solving 1-D Navier-Stokes equations or using
predetermined uniform velocity fields \cite{krepel_dyn3d-msr_2007,
kophazi_development_2009}. In more recent years, there has been
significant progress towards fully coupled, spatial codes that feature
2-D axisymmetric or full 3-D models. In 2011, Cammi et al.
\cite{cammi_multi-physics_2011} performed a ``\gls{MPM}'' analysis
of a simplified 2-D axisymmetric model of a single \gls{MSBR} fuel channel
using the commercial finite element analysis software COMSOL Multiphysics. The
physics were implemented through the two-group neutron diffusion equations,
and the \gls{RANS} standard $k$-$\epsilon$ turbulence model, for the
neutronics and thermal-hydraulics respectively. The
authors emphasized the need for proper full coupling of the multiphysics and
presented both steady-state and transient results in various
scenarios such as reactivity insertions, changes in pumping rate, and the
presence of periodic perturbations. This approach was featured again in a
later paper by Fiorina et al. \cite{fiorina_modelling_2014} in 2014 for a 2-D
axisymmetric model of the
\gls{MSFR}. The authors presented results from the Politecnico di Milano
COMSOL-based approach, and another approach by researchers from Delft
University of Technology, in which they coupled their in-house neutronics and
thermal-hydraulics codes, DALTON and HEAT respectively. With multigroup
neutron diffusion and \gls{RANS} formulations on ultra fine meshes, both
models agreed on the steady-state neutron flux, temperature,
and \gls{DNP} distributions, as well as the power responses following various
accident transient initiations. Aufiero et al. \cite{aufiero_development_2014}
concurrently developed
a full-core 3-D model of the \gls{MSFR} in OpenFOAM, albeit with one-group
neutron diffusion to reduce computational load. With the 3-D model, the
authors could simulate the asymmetric reactor response to the failure of a
single pump in the sixteen-pump \gls{MSFR} configuration. The authors also
provided quantitative data supporting the use of implicit coupling over
explicit coupling to obtain accurate solutions of the transient cases.
Recognizing the huge computational burden required for full 3-D simulations, 
later authors came up with innovative ways to alleviate this issue. Methods
include
selective geometrical reduced order modeling for various components of a
reactor based on the importance of the physical phenomena being simulated
\cite{zanetti_geometric_2015}, or using a novel, efficient method for
neutronics calculations \cite{laureau_transient_2017}.

\section{Molten Salt Fast Reactor}

The \gls{MSFR} is a European reference fast-spectrum \gls{MSR} concept
\cite{mathieu_thorium_2006, merle_optimized_2007}. Table \ref{table:msfr} and
Figure \ref{fig:msfr} show the main specifications and schematic view of the
\gls{MSFR}, respectively. Developed from the \gls{MSBR} design, the
\gls{MSFR} is intended to run primarily on a closed thorium fuel cycle with
continuous online fuel reprocessing. Several reasons motivated the omission of
graphite moderators from the original \gls{MSBR} design. Firstly, graphite is
susceptible to
long-term radiation damage and replacement is likely to be necessary during
the operating lifetime of the reactor. Secondly, graphite also has a positive
temperature coefficient of reactivity; eliminating graphite from the design
ensures a greater safety margin \cite{mathieu_thorium_2006}. Lastly, while
negative temperature coefficients are attainable with very thermalized
spectra, breeding ratios deteriorated significantly due to parasitic
absorption in the graphite \cite{mathieu_thorium_2006}.
%
\begin{figure}[htb!] 
	\centering
	\includegraphics[width=0.8\textwidth]{MSFR}
	\caption{Schematic view of the MSFR concept. Figure reproduced from
	Brovchenko et al. \cite{brovchenko_design-related_2013}.}
	\label{fig:msfr}
\end{figure}
%
\begin{table}[htb!]
    \small
	\caption{Main specifications of the \gls{MSFR} concept
				\cite{serp_molten_2014}.}
	\centering
	\begin{tabular}{ l r }
		\toprule
		Parameter & Value \\
		\midrule
		Thermal/Electric output [MW$_{\text{th}}$/MW$_{\text{e}}$] & 3000 /
		1300 
		\\
		Salt volume [m$^3$] & 18 \\
		Salt fraction in core & 0.5 \\
		Number of circulation loops & 16 \\
		Nominal flow rate [kg s$^{-1}$] & 18500  \\
		Nominal circulation time [s] & 4.0 \\
		Inlet/outlet temperature [K] & 923 / 1023 \\
		Blanket volume [m$^3$] & 7.3\\
		\bottomrule
	\end{tabular}
	\label{table:msfr}
\end{table}

@@

Although the \gls{MSFR} is primarily designed to operate on the thorium fuel
cycle, it supports a range of start-up fuel and feed compositions. This
versatility is particularly important for the first few \glspl{MSFR} to be
deployed due to the lack of $^{233}$U reserves required for the initial core
loading. In general, the fuel and blanket salts are approximately composed of
eutectic mixtures of 77.5\% LiF - 22.5\% AcF$_4$; AcF$_4$ represents
actinide fluorides such as uranium, thorium, plutonium, and other \gls{TRU}
fluorides.  For an initial composition consisting of $^{232}$Th and $^{233}$U,
the benchmark value for the amount of $^{233}$U for criticality under
normal operating conditions is 2.5 mol\%. However, a neutronic benchmark
study by Brovchenko et al. \cite{brovchenko_neutronic_2019} shows that
different neutronics software with different nuclear data provide
different $k_{eff}$ estimates even with the same isotopic compositions and
temperature distributions. The individual co-authors adjusted the
ratio of $^{232}$Th to $^{233}$U slightly to achieve exact criticality at a
uniform temperature of 973 K for their own neutronics software
\cite{brovchenko_neutronic_2019}. This thesis
performs the same exercise to adjust the inlet and outlet temperatures to
match nominal values.

@@

The present work uses the same 2-D square-cylindrical \gls{MSFR} design to
compare our results to results published by Fiorina et al.
\cite{fiorina_modelling_2014}. The design is a 2-D axisymmetric representation
of the \gls{MSFR} with the sixteen individual external loops homogenized into
a single outer loop as shown in Figure \ref{fig:msfrgeom}. For the multigroup
group constants calculations in Serpent, the 2-D axisymmetric model is
extended into a 3-D model by a 360-degree rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model \cite{brovchenko_neutronic_2019}. Accordingly, the
pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this is an approximation,
the outer loop is shielded from the core by a layer of boron carbide and sees
sufficiently low neutron fluxes that we may neglect its exact neutronics.
%
\begin{figure}[t!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}

@@

The reference start-up salt composition for the fuel and blanket salts is
77.5\% LiF - 22.5\% AcF$_4$ (actinide fluorides)
\cite{merle-lucotte_launching_2011}. Some researchers working with the
\gls{MSFR} model tweak the exact actinide composition by varying the
$^{232}$Th to $^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a
uniform temperature of 973 K \cite{brovchenko_neutronic_2019} or for other
unmentioned reasons \cite{fiorina_molten_2013}. Thus, the exact
actinide compositions vary depending on the nuclear data library, neutron
transport code, and the purpose of the study. The present work uses
a fuel salt composition of 77.5\% LiF - 19.913\% ThF$_4$ - 2.587\%
$^{233}$UF$_4$ for all calculations, which gives steady-state inlet and outlet
temperatures approximately equal to the nominal values in Table
\ref{table:msfr}. Table \ref{table:prip} shows relevant physical properties of
the fuel and blanket salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$
\cite{brovchenko_neutronic_2019}.}
\begin{tabular}{l l r r}
\toprule
Property & Formula & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $1.015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $0.01010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1594$ & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}

>>>>

Two other \gls{MSR} designs emerged in the 1970s: the \gls{DMSR} from
\gls{ORNL} \cite{gehin_liquid_2016} and the \gls{MCFR} from the UK Atomic
Energy Authority \cite{smith_assessment_1974}. \gls{ORNL}
researchers developed the \gls{DMSR}, named after its planned use of denatured
$^{235}$U fuel (i.e. low-enriched uranium), as a once-through converter system
without fuel reprocessing in response to fuel reprocessing restrictions
introduced by President Ford in 1976. On the other hand, UK researchers
developed the lead-cooled \gls{MCFR} to enhance $^{239}$Pu breeding with the
relatively fast neutron spectrum. Both designs failed to gain traction and did
not inspire any working prototypes.

Following a lull lasting through the late 20th century, researchers at
\gls{CNRS} began research into \glspl{MSR} in 1997
\cite{heuer_simulation_2010}. Starting from the \gls{MSBR} design, they
performed parametric studies on the design based on safety, breeding, and
other performance metrics \cite{mathieu_thorium_2006}. Their efforts
culminated in the \gls{MSFR} concept, a fast-spectrum breeder \gls{MSR}
designed to run on the thorium fuel cycle \cite{merle_optimized_2007}. In
2008, the Generation IV International Forum highlighted the \gls{MSFR} among
other \gls{MSR} designs for further development \cite{gif_generation_2008}.
The \gls{MSFR} has also benefited from collaborative research through two
European-funded projects, the EVOL and SAMOFAR projects
\cite{euratom_final_2015}. Today, numerous other national and commercial
bodies are also developing their own \gls{MSR} designs.

@@

The various \gls{MSR} designs under development today illustrate the
flexibility of this reactor concept. Graphite-moderated thermal-spectrum
\glspl{MSR} are typically straightforward \gls{LEU} burners or
$^{232}$Th/$^{233}$U iso-breeders/breeders, while epithermal- and
fast-spectrum \glspl{MSR} can operate as \gls{TRU} fuel burners or
$^{238}$U/$^{239}$Pu breeders. Breeder designs can be further categorized into
one- or two-fluid designs. Two-fluid designs feature separate blanket molten
salt mixtures that contain higher proportions of fertile material than the
fuel salt mixture. Examples of one-fluid designs include the Integral Molten
Salt Reactor from Terrestrial Energy \cite{leblanc_integral_2015} and the
\gls{MSR} design from Transatomic Power
\cite{transatomic_power_corporation_technical_2016} while two-fluid designs
include the \gls{MSFR} \cite{merle_optimized_2007} and \gls{MOSART}
\cite{ignatiev_molten_2014}. The current work involves simulations of
the \gls{MSFR} in Moltres and Section \ref{sec:msfr} describes this reactor
design in further detail.

@@

In terms of technological readiness, \glspl{MSR} still require significant
research efforts and experiments for the validation of
various components before a full commercial model can be commissioned. Work
towards creating a safety and licensing framework for \glspl{MSR} has picked
up pace only in recent years due to the growing interest from commercial
\gls{MSR} developers.

@@

In the past two decades, researchers have developed several
new tools for simulating steady-state and transient behavior in \glspl{MSR}.
Earlier efforts featured simplifications in simulating
thermal-hydraulics by using predetermined 1-D velocity fields. One such effort
\cite{krepel_dyn3d-msr_2007} used DYN3D-MSR, an \gls{MSR} simulation tool
adapted from the \gls{LWR} simulation tool DYN3D while another
\cite{kophazi_development_2009} adapted DALTON, originally a simulation
tool for high-temperature reactors. Both works studied the \gls{MSRE} and
simulated flow through advection terms in the temperature and precursor
equations in conjunction with full 3-D calculations for neutron flux and heat
conduction.

In more recent years, there has been
significant progress towards fully coupled, spatial codes that feature
2-D axisymmetric or full 3-D models. In 2011, Cammi et al.
\cite{cammi_multi-physics_2011} performed a ``\gls{MPM}'' analysis
of a simplified 2-D axisymmetric model of a single \gls{MSBR} fuel channel
using the commercial finite element analysis software COMSOL Multiphysics. The
physics were implemented through the two-group neutron diffusion equations,
and the \gls{RANS} standard $k$-$\epsilon$ turbulence model, for the
neutronics and thermal-hydraulics respectively. The
authors emphasized the need for proper full coupling of the multiphysics and
presented both steady-state and transient results in various
scenarios such as reactivity insertions, changes in pumping rate, and the
presence of periodic perturbations. Nagy et al. \cite{nagy_steady-state_2014}
introduced an improved version of DALTON which coupled with a \gls{CFD}
application and incorporated incompressible
Navier-Stokes flow to simulate salt flow more accurately. The authors
validated their model against \gls{MSRE} experimental data before presenting
multiphysics simulation results of a different graphite-moderated breeder
\gls{MSR}.

Both DALTON and the COMSOL-based tool featured again in a later paper by
Fiorina et al.
\cite{fiorina_modelling_2014} in 2014 for a 2-D axisymmetric model of the
\gls{MSFR}. The authors compared \gls{MSFR} simulations results from both
tools, in which they dubbed the COMSOL and DALTON/HEAT tools the Polimi and
TUDelft models, respectively, after the universities where each tool was
developed. With multigroup
neutron diffusion and \gls{RANS} formulations on ultra fine meshes, both
models agreed on the steady-state neutron flux, temperature,
and \gls{DNP} distributions, as well as the power responses following various
accident transient initiations. Aufiero et al. \cite{aufiero_development_2014}
concurrently developed
a full-core 3-D model of the \gls{MSFR} in OpenFOAM, albeit with one-group
neutron diffusion to reduce computational load. With the 3-D model, the
authors could simulate the asymmetric reactor response to the failure of a
single pump in the sixteen-pump \gls{MSFR} configuration. Aufiero et al. also
provided quantitative data supporting the use of implicit coupling over
explicit coupling to obtain accurate solutions of the transient cases.

Separately, Zhang et al. \cite{zhang_couple_2014} introduced another
self-contained \gls{MSR} simulation tool named COUPLE. Similar to the COMSOL
and OpenFOAM-based models, COUPLE solves the multigroup neutron diffusion
equations and the incompressible Navier-Stokes equations with the
$k$-$\epsilon$ turbulence model. The authors verified COUPLE's neutronics and
thermal-hydraulics against MCNP and a FLUENT-based model, respectively, before
presenting their multiphysics steady-state results with a 2-D axisymmetric
model of the \gls{MSFR}.

Recognizing the huge computational burden required for full 3-D simulations, 
some authors came up with innovative ways to alleviate this issue. Zanetti et
al. \cite{zanetti_geometric_2015} introduced a geometric multiscale modeling
approach for various components of a reactor based on the importance of
the physical phenomena being simulated. The authors employed a 3-D 
single-channel model for the \gls{MSRE} core and modeled the other
regions in the reactor such as the upper and lower plenums and the heat
exchanger using a lumped parameter approach. They also applied flux
factorization to decouple the temporal and spatial components in the neutron
diffusion equation. Laureau et al. \cite{laureau_transient_2017} devised a
different method, focusing solely making neutronics calculations more
efficient while retaining OpenFOAM's \gls{CFD} capabilities. The authors
adapted fission matrices, commonly used in Monte Carlo neutronics
applications, for efficient transient calculations in a modified version of
Serpent 2 \cite{leppanen_serpent_2014} and coupled it with OpenFOAM for
multiphysics transient simulations of the \gls{MSFR}.

\section{Molten Salt Fast Reactor} \label{sec:msfr}

The \gls{MSFR} is a European reference fast-spectrum \gls{MSR} concept
\cite{mathieu_thorium_2006, merle_optimized_2007}. Table \ref{table:msfr} and
Figure \ref{fig:msfr} show the main specifications and schematic view of the
\gls{MSFR}, respectively. Developed from the \gls{MSBR} design, the
\gls{MSFR} is intended to run primarily on a closed thorium fuel cycle with
continuous online fuel reprocessing. Several reasons motivated the omission of
graphite moderators from the original \gls{MSBR} design. Firstly, graphite is
susceptible to
long-term radiation damage and replacement is likely to be necessary during
the operating lifetime of the reactor. Secondly, graphite also has a positive
temperature coefficient of reactivity; eliminating graphite from the design
ensures a greater safety margin \cite{mathieu_thorium_2006}. Lastly, while
negative temperature coefficients are attainable with very thermalized
spectra, breeding ratios deteriorated significantly due to parasitic
absorption in the graphite \cite{mathieu_thorium_2006}.
%
\begin{figure}[htb!] 
	\centering
	\includegraphics[width=0.8\textwidth]{MSFR}
	\caption{Schematic view of the MSFR concept. Figure reproduced from
	Brovchenko et al. \cite{brovchenko_design-related_2013}.}
	\label{fig:msfr}
\end{figure}
%
\begin{table}[htb!]
    \small
	\caption{Main specifications of the \gls{MSFR} concept
				\cite{merle_concept_2017}.}
	\centering
	\begin{tabular}{ l r }
		\toprule
		Parameter & Value \\
		\midrule
		Thermal/Electric output [MW$_{\text{th}}$/MW$_{\text{e}}$] & 3000 /
		1300 
		\\
		Salt volume [m$^3$] & 18 \\
		Salt fraction in core & 0.5 \\
		Number of circulation loops & 16 \\
		Nominal flow rate [kg s$^{-1}$] & 18500  \\
		Nominal circulation time [s] & 4.0 \\
		Inlet/outlet temperature [K] & 923 / 1023 \\
		Blanket volume [m$^3$] & 7.3\\
		\bottomrule
	\end{tabular}
	\label{table:msfr}
\end{table}

@@

Although the \gls{MSFR} is primarily designed to operate on the thorium fuel
cycle, it supports a range of start-up fuel and feed compositions. This
versatility is particularly important for the first few \glspl{MSFR} to be
deployed due to the lack of $^{233}$U reserves required for the initial core
loading. In general, the fuel and blanket salts are approximately composed of
eutectic mixtures of 77.5\% LiF - 22.5\% AcF$_4$; AcF$_4$ represents
actinide fluorides such as uranium, thorium, plutonium, and other \gls{TRU}
fluorides. Using fluoride salts instead of chloride salts results in a
relatively thermal neutron spectrum. Therefore, the \gls{MSFR} has a more
thermal neutron spectrum than a typical sodium fast reactor. For an initial
composition consisting of $^{232}$Th and $^{233}$U,
the benchmark value for the amount of $^{233}$U for criticality under
normal operating conditions is 2.5 mol\%. However, a neutronic benchmark
study by Brovchenko et al. \cite{brovchenko_neutronic_2019} shows that
different neutronics software with different nuclear data provide
different $k_{eff}$ estimates even with the same isotopic compositions and
temperature distributions. The individual co-authors adjusted the
ratio of $^{232}$Th to $^{233}$U slightly to achieve exact criticality at a
uniform temperature of 973 K for their own neutronics software
\cite{brovchenko_neutronic_2019}. This thesis
performs the same exercise to adjust the inlet and outlet temperatures to
match nominal values.

@@

The present work uses the same 2-D square-cylindrical \gls{MSFR} design to
compare our results to results published by Fiorina et al.
\cite{fiorina_modelling_2014}. The design is a 2-D axisymmetric representation
of the \gls{MSFR} with the sixteen individual external loops homogenized into
a single outer loop as shown in Figure \ref{fig:msfrgeom}. For the multigroup
group constants calculations in Serpent, the 2-D axisymmetric model is
extended into a 3-D model by a 360-degree rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model \cite{brovchenko_neutronic_2019}. Accordingly, the
pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this is an approximation,
the outer loop is shielded from the core by a layer of boron carbide and sees
sufficiently low neutron fluxes that we may neglect its exact neutronic
properties.
%
\begin{figure}[t!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}

@@

The reference start-up salt composition for the fuel and blanket salts is
77.5\% LiF - 22.5\% AcF$_4$ (actinide fluorides)
\cite{merle-lucotte_launching_2011}. Some researchers working with the
\gls{MSFR} model tweak the exact actinide composition by varying the
$^{232}$Th to $^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a
uniform temperature of 973 K \cite{brovchenko_neutronic_2019} or for other
motivations \cite{fiorina_molten_2013} \cite{pettersen_coupled_2016}. Thus,
the exact actinide compositions vary depending on the nuclear data library,
neutron transport code, and the purpose of the study. The present work uses
a fuel salt composition of 77.5\% LiF - 19.913\% ThF$_4$ - 2.587\%
$^{233}$UF$_4$ for all calculations, which gives steady-state inlet and outlet
temperatures approximately equal to the nominal values in Table
\ref{table:msfr}. Table \ref{table:prip} shows relevant physical properties of
the fuel and blanket salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$
\cite{brovchenko_neutronic_2019}.}
\begin{tabular}{l l r r}
\toprule
Property & Formula & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $0.01015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $1.010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1594$ & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}
